%-----------EXPERIENCE-----------%
\section{Experience}
\resumeSubHeadingListStart

    \resumeSubheading
    {Peraton Labs}{Jun 2026 -- Present}
    {Senior Associate Research Scientist}{Remote}
    
    \resumeSubheading
    {Peraton Labs}{Aug 2025 -- May 2026}
    {AI Research Science Intern}{Herndon, VA}
    \resumeItemListStart
        \resumeItem{Implemented a social media agent allowing  users to query millions of social media documents through natural language via agentic control of the Babel Street API. Optimized search results with similarity metrics.}
        \resumeItem{Developed resilient skills-based agentic workflows with Temporal.io for reproducible custom tooling.}
        \resumeItem{Architected and deployed an S3-based data lake as a scalable plugin to support terabytes of user documents.}
    \resumeItemListEnd
    \resumeSubheading
    {Peraton}{Jan 2025 -- Aug 2025}
    {Software Engineering Intern}{Herndon, VA}
    \resumeItemListStart
        \resumeItem{Built Python based LLM agents with Retrieval Augmented Generation (RAG), tool calling, and iterative workflows.}
        \resumeItem{Engineered a persistent memory system using PostgreSQL to enable agents to recall user-specific data and tailor responses with long term context. Utilized diff-based rewrites, reducing token count by up to 90\%.}
        \resumeItem{Developed analytics infrastructure to track token usage, cost, and user behavior across the LLM platform, supporting customer budgeting and system monitoring. Enabled usage-based account throttling to prevent system abuse.}
        \resumeItem{Created a corresponding analytics agent that converts user prompts into SQL queries, outputs to CSV, and executes python to create insights and generate graph visualizations, saving customers thousands of dollars in tokens.}
    \resumeItemListEnd
    
    \resumeSubheading
    {BrightVine Solutions}{May 2023 -- Aug 2023, May 2024 -- Aug 2024}
    {Software Engineering Intern}{Remote}
    \resumeItemListStart
        \resumeItem{Built an Azure OpenAI integrated chatbot that converts natural language to SQL with client specific fine-tuning.}
        \resumeItem{Designed and deployed a batch import error handling system using SQL, C\#, and XML to production.}
    \resumeItemListEnd
    
    \resumeSubheading
    {Virginia Tech Department of Computer Science}{Jan 2023 -- Dec 2024}
    {Teaching Assistant, CS 1064: Intro to Python}{Blacksburg, VA}
    \resumeItemListStart
        \resumeItem{Supported 2000+ students by mentoring, debugging, and answering questions on foundational Python coding.}
    \resumeItemListEnd

\resumeSubHeadingListEnd